### 2019-03-20 _publications/jors/paper.tex
Add Tonks as author
Update for stvdwtt review

%% Set the header information
\pagestyle{fancy}
\definecolor{mygray}{gray}{0.6}
\renewcommand\headrule{}
\rhead{\footnotesize 3}

@@

@@

1. Wheeler, Daniel; (corresponding author) A\\
2. Keller, Trevor; A\\
3. DeWitt, Stephen J.; E\\
4. Jokisaari, Andrea M.; D\\
5. Schwen, Daniel; D\\
6. Guyer, Jonathan E.; A\\
7. Aagesen, Larry; D\\
8. Heinonen, Olle G.; B\\
9. Voorhees, Peter W.; C\\
10. Warren, James A.; G

@@

F. Materials Science and Engineering Department, \\
University of Michigan, \\
Ann Arbor, MI 48109 USA

G. Material Measurement Laboratory Office, \\
Material Measurement Laboratory, \\
National Institute of Standards and Technology,\\
Gaithersburg, MD 20899 USA

@@

Scientific research communities often require an online portal to
summarize a shared challenge, collect attempts at a solution, and
present a quantitative comparison of past attempts in a compelling
way. An exemplar of such a portal is
$\mu$MAG~\cite{mumag}~\footnote{Certain commercial equipment,
  instruments, or materials (or suppliers, or software, ...) are
  identified in this paper to foster understanding. Such
  identification does not imply recommendation or endorsement by the
  National Institute of Standards and Technology, nor does it imply
  that the materials or equipment identified are necessarily the best
  available for the purpose.\label{disclaimer}}. The reusable PFHub
framework leverages existing online services to build a static portal
website that is considerably easier to deploy and maintain without
sacrificing content or scope. The first deployment of the PFHub
framework supports phase-field practitioners and code developers
participating in an effort to improve quality assurance for
phase-field codes.

@@

The phase-field method (PFM) describes material interfaces at the
mesoscopic scale between atomic scale models and macroscale models.
The PFM is well established and there are an assortment of code
frameworks (\emph{e.g.}, Moose~\cite{moose},
PRISMS-PF~\cite{prisms-pf}, FiPy~\cite{fipy},
MMSP~\cite{mmsp}~\textsuperscript{\ref{disclaimer}}) available for
solving the wide variety of phenomena associated with phase-field
(\emph{e.g.}, dendritic growth, spinodal decomposition, grain
growth). However, phase-field research groups often develop codes in
isolation and do not publish the code bases or do not support or
distribute the code bases for the wider community. PFHub is a
community effort spearheaded by the Center for Hierarchical Materials
Design at Northwestern University and the National Institute of
Standards and Technology to support the development of phase field
codes. In particular, the PFHub effort focuses on improving
cross-collaboration between phase-field code developers and
practitioners by providing a standardized set of benchmark
problems~\cite{bm1, bm2} along with a web framework for uploading and
comparing benchmark results from different codes.

@@

The PFHub website provides a facility for uploading, displaying and
comparing results from the benchmark problems. The website uses the
Jekyll static website generator~\cite{jekyll} along with automated
frontend processing to eliminate the need for content management
systems~\cite{cmsfree}, which are generally costly to maintain
especially for small scientific communities with limited funding and
manpower.

@@

A combination of Jekyll templates and Coffeescript are used to access
and download the data links in the submitted YAML files and then
display the data in interactive figures on the website. The
combination of a central repository on GitHub for website source code
and metadata with distributed data records on third-party archives
avoids the complexity and administrative overhead of maintaining a
live database and associated back-end application. The PFHub
infrastructure provides a template for other small scientific
communities to host custom content and integrate data from members of
their community.

@@

The PFHub framework can be deployed on any platform supporting Nix,
which includes all contemporary Linux and Mac OS X platforms. However,
since the framework is built with Jekyll and automated front-end
processing it can be deployed on GitHub's Pages infrastructure.

@@

\begin{itemize}
  \item Upload new benchmark defintions in a format that Jekyll can
    parse, \emph{e.g.}, Jupyter Notebook, Markdown or HTML.
  \item Edit the \texttt{benchmarks.yaml} file to reflect the new
    upload requirements and describe the figures that need to be
    generated on the upload comparison pages.
  \item Edit the \texttt{\_config.yml} file to update links and text
    related to the configuration for all aspects of the website.
  \item Update Markdown files to reflect the new content and mission
    of the scientific community.
  \item Remove data and files that are not required by the new
    community.
\end{itemize}

@@

D.W. wishes to acknowledge the Materials Genome Initiative funding
allocated to the National Institute of Standards and Technology.

>>>>

%% Set the header information
\pagestyle{fancy}
\definecolor{mygray}{gray}{0.6}
\renewcommand\headrule{}

@@

\setlength{\parskip}{\baselineskip}%
\setlength{\parindent}{0pt}%

@@

1. Wheeler, Daniel; (corresponding author) A\\
2. Keller, Trevor; A\\
3. DeWitt, Stephen J.; E\\
4. Jokisaari, Andrea M.; D\\
5. Schwen, Daniel; D\\
6. Guyer, Jonathan E.; A\\
7. Aagesen, Larry; D\\
8. Heinonen, Olle G.; B\\
9. Tonks, Michael R.; G\\
10. Voorhees, Peter W.; C\\
11. Warren, James A.; F

@@

F. Material Measurement Laboratory Office, \\
Material Measurement Laboratory, \\
National Institute of Standards and Technology,\\
Gaithersburg, MD 20899 USA

G. Department of Materials Science and Engineering, \\
University of Florida, \\
Gainesville, FL 32611

@@

An online portal provides a valuable space for scientific communities
to summarize a shared challenge, collect attempts at a solution, and
present a quantitative comparison of past attempts in a compelling
way. An exemplar of such a portal is
$\mu$MAG~\cite{mumag}~\footnote{Certain commercial equipment,
  instruments, or materials (or suppliers, or software, ...) are
  identified in this paper to foster understanding. Such
  identification does not imply recommendation or endorsement by the
  National Institute of Standards and Technology, nor does it imply
  that the materials or equipment identified are necessarily the best
  available for the purpose.\label{disclaimer}}. The reusable PFHub
framework leverages existing online services to build a static portal
website that is considerably easier to deploy and maintain without
sacrificing content or scope. The first deployment of the PFHub
framework supports phase-field practitioners and code developers
participating in an effort to improve quality assurance for
phase-field codes.

@@

The phase-field method (PFM) describes material interfaces at the
mesoscopic scale between atomic scale models and macroscale models.
The PFM is well established and there are an assortment of code
frameworks (\emph{e.g.}, MOOSE~\cite{moose},
PRISMS-PF~\cite{prisms-pf}, FiPy~\cite{fipy},
MMSP~\cite{mmsp}~\textsuperscript{\ref{disclaimer}}) available for
solving the wide variety of phenomena associated with the PFM
(\emph{e.g.}, dendritic growth, spinodal decomposition, grain
growth). However, phase-field research groups often develop codes in
isolation and do not support or distribute the code bases to the wider
community. PFHub is a community effort spearheaded by the Center for
Hierarchical Materials Design at Northwestern University and the
National Institute of Standards and Technology to support the
development of phase-field codes. In particular, the PFHub effort
focuses on improving cross-collaboration between phase-field code
developers and practitioners by providing a standardized set of
benchmark problems~\cite{bm1, bm2} along with a web framework for
uploading and comparing benchmark results from different codes.

@@

The PFHub website provides a facility for uploading, displaying and
comparing results from the benchmark problems. The website uses the
Jekyll static website generator~\cite{jekyll} along with automated
frontend processing to eliminate the need for content management
systems~\cite{cmsfree}, which are generally costly to maintain
especially for small scientific communities with limited funding and
staffing.

@@

A combination of Jekyll templates and Coffeescript are used to access
and download the data links in the submitted YAML files and then
display the data in interactive plots on the website.  Previous
iterations of PFHub used the Vega JSON Library~\cite{vega} to generate
the interactive plots, but now the Plotly JavaScript Graphing
Library~\cite{plotly} is used exclusively as it provides a more
programmable interface and requires less upfront configuration.

The benchmark specifications consist of equations, narrative, plots
and code samples; and are composed in Jupyter Notbooks. The Jupyter
Notebooks are included as static objects in the website after
translation into HTML using the nbconvert tool~\cite{jupyter}.

The combination of a central repository on GitHub for website source
code and metadata with distributed data records on third-party
archives avoids the complexity and administrative overhead of
maintaining a live database and associated back-end application. The
PFHub infrastructure provides a template for other small scientific
communities to host custom content and integrate data from members of
their community.

@@

The PFHub framework can be deployed on any platform supporting Nix,
which includes all contemporary Linux and Mac OS X platforms. Since
the framework is built with Jekyll and automated front-end processing,
it can be deployed on GitHub's Pages infrastructure, which enables
streamlined deployment without the need for any back-end
infrastructure.

@@

\begin{itemize}
  \item Upload new benchmark definitions in a format that Jekyll can
    parse, \emph{e.g.}, Jupyter Notebook, Markdown or HTML.
  \item Edit the \texttt{benchmarks.yaml} file to reflect the new
    upload requirements and describe the figures that need to be
    generated on the upload comparison pages.
  \item Edit the \texttt{\_config.yml} file to update links and text
    related to the configuration for all aspects of the website.
  \item Update Markdown files to reflect the new content and mission
    of the scientific community.
  \item Remove data and files that are not required by the new
    community.
\end{itemize}

@@

D.W. wishes to acknowledge the Materials Genome Initiative funding
allocated to the National Institute of Standards and Technology. S.J.D
wishes to acknowledge funding from the U.S. Department of Energy,
Office of Basic Energy Sciences, Division of Materials Sciences and
Engineering under Award \#DE-SC0008637 as part of the Center for
PRedictive Integrated Structural Materials Science (PRISMS Center) at
University of Michigan.
